---
title: "Homework 2"
author: "Jiao Qu A20386614, Yuan-An Liu A20375099, Zhenyu Zhang A20287371 "
output:
  pdf_document: default
  html_document: default
---
```{r setup, include=FALSE}
LoadLibraries = function (){
  # load libraries
  library(ISLR)
  library(MASS)
  print("The libraries have been loaded .")
}

LoadLibraries()
```
# Q8.
## (a)
```{r}
summary(Auto)
lm.fit =lm(mpg~horsepower ,data=Auto)
summary(lm.fit)
```
i. Yes, p-value of the F-statistic is close to 0.  
ii. Strong relationship.The mean of mpg is 23.45. Because of the RSE is 4.906 , it shows the percentage error of close to 20%. So A huge percentage of the variance in mpg is explained by horsepower.  
iii. The relationship between mpg and horsepower is "Negative"  

iv.  
```{r}
# the predicted mpg associated with a horsepower of 98
predict(lm.fit, data.frame(horsepower=c(98)))
# the associated 95% confidence interval
predict(lm.fit, data.frame(horsepower=c(98)), interval = "confidence")
# the associated 95% prediction interval
predict(lm.fit, data.frame(horsepower=c(98)), interval = "prediction")
```

## (b)

```{r, echo=FALSE, message=FALSE}
attach(Auto) # for plot
plot(horsepower, mpg)
abline(lm.fit)
abline(lm.fit,lwd =3, col ="red")
```

## (c)

```{r, echo=FALSE}
plot(lm.fit)
```

# Q9.
## (a)

```{r}
pairs(Auto) # scatterplot matrix
```

## (b)

```{r}
cor(Auto[,1:8]) # correlations between the variables without names
```

## (c)

```{r}
lm.fit =lm(mpg~.-name,data=Auto)
summary(lm.fit)
```

i.  Yes  
ii. displacement, weight, year and origin  
iii. Regression coefficient of year: 0.75 The lower the "year" (older), the higher the "mpg"  

## (d)

```{r,  echo=FALSE}
plot(lm.fit)
plot(predict(lm.fit), rstudent(lm.fit))
```

- The fit seems not linear. There is a curve.  
- There are some values in "rstudent" > 3   

## (e)

```{r}
Auto2 = Auto[,1:8]
lm2.fit = lm(mpg~.*., data = Auto2)
summary(lm2.fit)
```

From the p-values, e.g. acceleration:origin is statistically signifcant

## (f)

```{r, echo=FALSE, message=FALSE}
attach(Auto)
plot(log(horsepower), mpg)
plot(sqrt(horsepower), mpg)
plot((horsepower)^2, mpg)
```

It shows that "log" is a better fit than the original one.  

# Q10.
## (a)

```{r}
lm.fit =lm(Sales~Price + Urban + US, data = Carseats)
summary(lm.fit)
```

## (b)
#####Price  
- According to the linear regression, there is a relationship. he higher price, the lower sales.  

#####urbanYes  
- According to the linear regression, there isn’t a relationship between the location of the store and the number of sales  

#####USYes  
- According to the linear regression, there is a relationship. If the store is in the US, the sales will increase.  

## (c)

Sales = 13.04 + -0.05 Price + -0.02 UrbanYes + 1.20 USYes  

## (d)

Price and USYes  

## (e)

```{r}
#uses the predictors for which there is evidence of association with the outcome
lm2.fit = lm(Sales~Price + US, data = Carseats)
summary(lm2.fit)
```

## (f)

```{r}
summary(lm.fit)
```

Comparing to lm2.fit, the two models are similarly fit.  

## (g)

```{r}
# Confidence Intervals:
confint(lm2.fit)
```

## (h)

```{r, echo=FALSE}
plot(lm2.fit)
```

As the rstudents values, there is no outliers are suggested.  

```{r, echo=FALSE}
plot(predict(lm2.fit), rstudent(lm2.fit))
```

The graph shows that there are a few high leverage points.  

# Q13.

```{r}
set.seed(1)
```

set.seed(1) prior to starting part (a): according to the question  

## (a)

```{r}
x = rnorm(100, 0, 1)
```

## (b)

```{r}
eps = rnorm(100, 0, 0.25)
```

## (c)

```{r}
y = -1 + 0.5*x + eps
length(y)
summary(y)
```

length of vector y  = 100 ; beta0 = -1 ; beta1 = 0.5  

## (d)

```{r, echo=FALSE}
plot(x,y)
abline(lm.fit)
```

Linear relationship  

## (e)

```{r}
lm.fit = lm(y~x)
summary(lm.fit)
```

beta0 and 1 are similar to the original values.  

## (f)

```{r}
plot(x,y)
abline(lm.fit)
abline (lm.fit, lwd =3, col ="red")
```

## (g)

```{r}
lm2.fit = lm(y~poly(x, 2))
summary(lm2.fit)
```

Regression coefficient of the model is insignificant.  

## (h)

```{r}
set.seed(1)
eps = rnorm(100, 0, 0.1) # less noise
x = rnorm(100)
y = -1 + 0.5*x + eps
plot(x, y)
lm1.fit = lm(y~x)
summary(lm1.fit)
abline(lm1.fit, lwd =3, col ="red")
```

RSE dencreases  

## (i)
```{r}
set.seed(1)
eps = rnorm(100, 0, 0.5)  # more noise
x = rnorm(100)
y = -1 + 0.5*x + eps
plot(x, y)
lm2.fit = lm(y~x)
summary(lm2.fit)
abline(lm2.fit, lwd =3, col ="red")
```

RSE increases  

## (j)

```{r}
confint(lm.fit)
confint(lm1.fit)
confint(lm2.fit)
```

With different level of noises, Intervals are still around 0.5.  
